The \dealii{} Library, Version 8.5

### 2017-03-18 8.5/paper.tex
Added draft blurp on MappingManifold

TODO: Luca

>>>>

The \texttt{MappingManifold} class implements the same functionality
of the \texttt{Mapping} class for \emph{manifold conforming}
mappings. This class computes the transformation between the
reference and real cell by exploiting the geometrical information
coming from the underlying \texttt{Manifold} object.

Quadrature points computed using this mapping lie on the exact
geometrical objects, and tangent and normal vectors computed using
this class are tangent and normal to the underlying geometry. This is
in constrast with the \texttt{MappingQ} and \texttt{MappingQGeneric}
classes, which approximate the geometry using a polynomial of some
order, and then compute the normals and tangents using the
approximated surface.

Currently only first order transformations are implemented, and an
assertion is thrown if the user requests any higher order
transformations, for example, the hessian of the mapping.
